---
title: "Portfolio"
author: "Ramya Desineedi"
date: "16/08/2021"
output: pdf_document
---
## **Portfolio Modeling**
In this problem, we will construct three different portfolios of exchange-traded funds, or ETFs, and use bootstrap resampling to analyze the short-term tail risk of our portfolios.

```{r, echo=FALSE, include=FALSE}
library(ggstance)
library(mosaic)
library(quantmod)
library(foreach)

rm(list=ls())
```

We selected the ETFs ensuring diversity and different levels of risk. 

The Ivesco RSP trust is linked to the S&P 500 Index, however its unique weighting methodology will make it useful for some, while impractical for active traders. Like many Rydex products, RSP is linked to an equal-weighted index, meaning that component companies receive approximately equal allocations. That results in exposure that is considerably more balanced than other alternatives such as SPY, and a methodology that some investors believe will add value over the long haul. In return for this unique exposure you can expect higher fees; this ETF is considerably more expensive and less liquid than both SPY and IVV, though it is still extremely cost efficient compared to most mutual funds.

SPY is one of the safest and largest ETFs around.

First Trust Value Line Dividend Index Fund (FVD) has 20% allocated in Financial industry stocks. 

ProShares UltraShort FTSE Europe (EPV) is a low performing ETF for the past few years. 

iShares Core Growth Allocation ETF (AOR) is a very diverse ETF. 

In total, we have selected 6 ETFs - "RSP", "SPY", "FVD", "EPV", "AOR" and "YYY". We have considered 5 years of ETF data starting from 01-Jan-2015.

```{r, echo=FALSE, include=FALSE}
# Import a few stocks
mystocks = c("RSP", "SPY", "FVD", "EPV", "AOR", "YYY")
# Getting the price data for 5 years
getSymbols(mystocks, from='2015-01-01')
for(ticker in mystocks){
  expr = paste0(ticker, "a=adjustOHLC(", ticker, ")")
  eval(parse(text=expr))
}
```

```{r, echo=FALSE, include=FALSE}
# Computing the return matrix
all_returns = cbind( ClCl(RSPa),
                     ClCl(SPYa),
                     ClCl(FVDa),
                     ClCl(EPVa),
                     ClCl(AORa),
                     ClCl(YYYa))
head(all_returns)
```

```{r, echo=FALSE, include=FALSE}
# Remove NAs
all_returns = as.matrix(na.omit(all_returns))
head(all_returns)
```

Lets look at how the stocks are performing relative to each other using a pair scatterplot. 
```{r, echo=FALSE}
# checking the correlation
pairs(all_returns)
```

We can see a strong correlation among these ETFs.



#### Volatility of the ETFs across the 5 year period.
```{r, echo=FALSE}
# Volatility check
plot(ClCl(RSPa), type='l')
plot(ClCl(SPYa), type='l')
plot(ClCl(FVDa), type='l')
plot(ClCl(EPVa), type='l')
plot(ClCl(AORa), type='l')
plot(ClCl(YYYa), type='l')
```

```{r, echo=FALSE, include=FALSE}
initial_wealth = 100000
```

Our initial wealth is $100,000 

SIMULATION 1 : SAFE Portfolio

ETFs: "RSP", "SPY", "FVD", "EPV", "AOR", "YYY"

For the safe portfolio, we distributed 90% of the total wealth among the high performing ETFs - RSP, SPY and AOR.

Average return of investement after 20 days - $100915.5   
5% Value at Risk for safe portfolio - $6060.381   

```{r, echo=FALSE, include=FALSE}
sim1 = foreach(i=1:5000, .combine = rbind) %do% {
  weights = c(0.3, 0.4, 0.03, 0.03, 0.2, 0.04)
  total_wealth = initial_wealth
  holdings = total_wealth * weights
  n_days = 20
  wealthtracker = rep(0, n_days)
  
  for(today in 1:n_days){
    return_today = resample(all_returns, 1, orig.ids=FALSE)
    holdings = holdings * (1 + return_today)
    total_wealth = sum(holdings)
    wealthtracker[today] = total_wealth
    
    # Rebalancing
    holdings = total_wealth * weights
  }
  
  wealthtracker
}
head(sim1)
hist(sim1[,n_days], 50)
plot(density(sim1[,n_days]))
# Profit/loss
hist(sim1[,n_days]- initial_wealth, breaks=30)
conf_5Per = confint(sim1[,n_days]- initial_wealth, level = 0.90)$'5%'
cat('\nAverage return of investement after 20 days', mean(sim1[,n_days]), "\n")
cat('\n5% Value at Risk for safe portfolio-',conf_5Per, "\n")
```

```{r, echo=FALSE, include=FALSE}
wealth_daywise = c()
  
for (i in 1:n_days){
    wealth_daywise[i] = mean(sim1[,i]) 
}
days = 1:n_days
df = data.frame(wealth_daywise, days)
```


```{r, echo=FALSE}
ggplot(data=df, aes(x=days, y=wealth_daywise, group=1)) +
  geom_line(color="red")+
  geom_point() +
  xlab('Days') +
  ylab('Return of investments') + 
  ggtitle('Safe Portfolio: Retruns over 20 days')
```



```{r, echo=FALSE}
hist(sim1[,n_days], 50)
plot(density(sim1[,n_days]))
hist(sim1[,n_days]- initial_wealth, breaks=30)
conf_5Per = confint(sim1[,n_days]- initial_wealth, level = 0.90)$'5%'
cat('\nAverage return of investement after 20 days', mean(sim1[,n_days]), "\n")
cat('\n5% Value at Risk for safe portfolio-',conf_5Per, "\n")
```

SIMULATION 2 : HIGH RISK PORTFOLIO

For the high risk portfolio, we distributed 90% of the total wealth among the low performing ETFs - SVXY, EPV and YYY.

Average return of investement after 20 days - $100063.1  
5% Value at Risk for safe portfolio - $2811.46 

```{r, echo=FALSE, include=FALSE}
sim2 = foreach(i=1:5000, .combine = rbind) %do% {
  weights = c(0.01, 0.02, 0.3, 0.3, 0.07, 0.3)
  total_wealth = initial_wealth
  holdings = total_wealth * weights
  n_days = 20
  wealthtracker = rep(0, n_days)
  
  for(today in 1:n_days){
    
    return_today = resample(all_returns, 1, orig.ids=FALSE)
    holdings = holdings * (1 + return_today)
    total_wealth = sum(holdings)
    wealthtracker[today] = total_wealth
    
    # Rebalancing
    holdings = total_wealth * weights
  }
  
  wealthtracker
}
head(sim2)
hist(sim2[,n_days], 50)
plot(density(sim2[,n_days]))
# Profit/loss
hist(sim2[,n_days]- initial_wealth, breaks=30)
hist(sim2[,n_days]- initial_wealth, breaks=30)
conf_5Per = confint(sim2[,n_days]- initial_wealth, level = 0.90)$'5%'
cat('\nAverage return of investement after 20 days', mean(sim2[,n_days]), "\n")
cat('\n5% Value at Risk for High portfolio-',conf_5Per, "\n")
```


```{r, echo=FALSE, include=FALSE}
wealth_daywise = c()
  
for (i in 1:n_days){
    wealth_daywise[i] = mean(sim2[,i]) 
}
days = 1:n_days
df = data.frame(wealth_daywise, days)
```


```{r, echo=FALSE}
ggplot(data=df, aes(x=days, y=wealth_daywise, group=1)) +
  geom_line(color="red")+
  geom_point() +
  xlab('Days') +
  ylab('Return of investments') + 
  ggtitle('High Risk Portfolio: Retruns over 20 days')
```

```{r, echo=FALSE}
hist(sim2[,n_days], 50)
plot(density(sim2[,n_days]))
# Profit/loss
hist(sim2[,n_days]- initial_wealth, breaks=30)
conf_5Per = confint(sim2[,n_days]- initial_wealth, level = 0.90)$'5%'
cat('\nAverage return of investement after 20 days', mean(sim2[,n_days]), "\n")
cat('\n5% Value at Risk for High portfolio-',conf_5Per, "\n")
```



SIMULATION 3 - With equal weights for high risk and low risk

Average return of investement after 20 days - $100467.3 
5% Value at Risk for safe portfolio - $3111.25

```{r, echo=FALSE, include=FALSE}
sim3 = foreach(i=1:5000, .combine = rbind) %do% {
  weights = c(0.17, 0.17, 0.17, 0.17, 0.17, 0.15)
  total_wealth = initial_wealth
  holdings = total_wealth * weights
  n_days = 20
  wealthtracker = rep(0, n_days)
  
  for(today in 1:n_days){
    
    return_today = resample(all_returns, 1, orig.ids=FALSE)
    holdings = holdings * (1 + return_today)
    total_wealth = sum(holdings)
    wealthtracker[today] = total_wealth
    
    # Rebalancing
    holdings = total_wealth * weights
  }
  
  wealthtracker
}
head(sim3)
```



```{r, echo=FALSE}
hist(sim3[,n_days], 50)
plot(density(sim3[,n_days]))
# Profit/loss
hist(sim3[,n_days]- initial_wealth, breaks=30)
conf_5Per = confint(sim3[,n_days]- initial_wealth, level = 0.90)$'5%'
cat('\nAverage return of investement after 20 days', mean(sim3[,n_days]), "\n")
cat('\n5% Value at Risk for High risk portfolio-',conf_5Per, "\n")
```

```{r, echo=FALSE, include=FALSE}
wealth_daywise = c()
for (i in 1:n_days){
    wealth_daywise[i] = mean(sim3[,i]) 
}
days = 1:n_days
df = data.frame(wealth_daywise, days)
```


```{r, echo=FALSE}
ggplot(data=df, aes(x=days, y=wealth_daywise, group=1)) +
  geom_line(color="red")+
  geom_point() +
  xlab('Days') +
  ylab('Return of investments') + 
  ggtitle('Diverse Portfolio: Retruns over 20 days')
```

```{r, echo=FALSE}
hist(sim3[,n_days], 50)
plot(density(sim3[,n_days]))
# Profit/loss
hist(sim3[,n_days]- initial_wealth, breaks=30)
conf_5Per = confint(sim3[,n_days]- initial_wealth, level = 0.90)$'5%'
cat('\nAverage return of investement after 20 days', mean(sim3[,n_days]), "\n")
cat('\n5% Value at Risk for Medium risk portfolio-',conf_5Per, "\n")
```


#### **Summary**

For the safe portfolio, we are observing the maximum return of investment. For the high risk portfolio we are observing the lowest 5% VaR . 
As the portfolio risk increases, we are able to witness the decrease in returns and increase in VaR value as expected.





